Figures to insert in text

### 2018-04-10 Chapters/Chapter01.tex
Blockchain: Hathor's architecture.

The present work intends to analyze a new architecture, named Hathor, which lies between Bitcoin and Iota and may be a viable solution to both scaling, centralization, and spam problems. We also present a mathematical analysis of Bitcoin's architecture.

@@

This way, there will be two difficulty levels in the system: one for new transactions which are just moving tokens around, and another one for ``blocks'' which are generating new tokens and collecting fees. The first may be adjusted to prevent spammers, which would spend too many resources to generate a great number of new transactions. The second is adjusted every 2016 blocks to keep the pace of one block every 10 minutes.

@@

Each transaction has to confirm all its inputs, i.e., there must be a confirmation path between all the transactions of the inputs and the transaction which are spending them. It is always possible given that there is at least one confirmation path between any transaction and a tip.

@@

In Bitcoin, it is usually required 6 confirmations before accepting a transaction. Let $H$ be the total hash rate of the network. Then, as $\mathbf{E}(Y_6) = 60 \text{ minutes}$, it will be necessary to calculate, on average, $\mathbf{E}(Y_6) \cdot H = 60 \cdot 60 \cdot H$ hashes to solve the proof-of-work of 6 blocks. Finally, a transaction is said to be confirmed when its accumulated weight is greater than or equal to $\log_2(\mathbf{E}(Y_6) \cdot H) = \log_2(60 \cdot 60 \cdot H) = \log_2(3600) + \log_2(H) = 4 + \log_2(225) + \log_2(H)$, where $H$ is calculated as the total hash rate of the miners plus the total hash rate of new transactions.

\chapter{Proposal: Questions to be explored}
 The main question which this work proposes to answer is: Is it reliable to use DAG model? In which conditions?

@@

In this paper, we will analyze the network scaling and security. How a DAG network scales, simulating different loads and measuring the bandwidth, computational effort, and storage space necessary to handle all the transactions in time. What is the minimum transaction's aggregated weight which it may be considered unlikely to be reversed?

@@

As the DAG network is distributed, its users may use different parameters --- they cannot violate the network's rules, but they may use different tip selection algorithms, for instance. We would like to explore how different users' parameters may affect the network, how much is necessary to cause either a hard-fork or a soft-fork.

\cite{tangle2016} suggests that constraining transactions' weight in a range would both prevent spam, because it would be necessary a minimum work to propagate a new transaction, and attacks, because an attacker would not be allowed to propagate a transaction with very high weight. We agree with the spam argument, and would like how a minimum weight would affect mobile devices's new transactions. We partially agree with the upper bound, because an attacker would be able to generate many transaction with lower weight. We will analyze if constraining transactions' weight would be effective against nuclear submarine attacks.

We have another suggestion to prevent nuclear submarine attacks: set a maximum depth for the transactions confirmed by a new transaction. So, new transactions would have to confirming newer transactions instead of old transactions, and a nuclear submarine attack would be controlled because the attacker would be not be able to create a large separate DAG. But the maximum depth rule would possibly also affect transaction created by low (hash)power devices, because it would take a longer time to solve the proof-of-work and, if the confirmations are going fast, the transaction would possibly be invalidated. This raises another important question: what would be an optimal maximum depth allowed?

If we would like to include fee transactions, how would it be distributed between confirmations? As transactions may have multiple direct confirmations, it is not obvious who would receive the transaction fee. An intuitive suggestion would be to give the fee to the first confirmation with a minimum weight, but it might have some propagation problems, because it takes a while to propagate a transaction in the network and there would be conflict.

In order to solve the fee distribution problem, we will simulate how the network would behave if we include blocks. These blocks would be like Bitcoin's, with an adjustable proof-of-work according to the network's hashpower. They would receive the fees from all confirmed transactions which had not been confirmed by any block before, and they would be able to generate new coins. These blocks would also help solving other problems.

@@

\chapter{Analysis of DAG Model}

>>>>

The present work intends to propose and analyze a new architecture, named Hathor, which lies between Bitcoin and Iota and may be a viable solution to both scaling, centralization, and spam problems. We also present a mathematical analysis of Bitcoin's architecture.

@@

This way, there will be two difficulty levels in the system: one for new transactions which are just moving tokens around, and another one for ``blocks'' which are generating new tokens and collecting fees. The first may be adjusted to prevent spammers, which would spend too many resources to generate a great number of new transactions. The second is adjusted every 2,016 blocks to keep the pace of block on every 2 minutes.

@@

Each transaction has to confirm all its inputs, i.e., there must be a confirmation path between all the transactions of the inputs and the transaction which are spending them. It is always possible since there is at least one confirmation path between any transaction and a tip. This is important for security reasons.

@@

In Bitcoin, it is usually required 6 confirmations before accepting a transaction. Let $H$ be the total hash rate of the network. Then, as $\mathbf{E}(Y_6) = 60 \text{ minutes}$, it will be necessary to calculate, on average, $\mathbf{E}(Y_6) \cdot H = 60 \cdot 60 \cdot H$ hashes to solve the proof-of-work of 6 blocks. Therefore, in order to have the same level of security as Bitcoin, a transaction is said to be confirmed when its accumulated weight is greater than or equal to $\log_2(\mathbf{E}(Y_6) \cdot H) = \log_2(60 \cdot 60 \cdot H) = 4 + \log_2(225) + \log_2(H)$, where $H$ is calculated as the total hash rate of the miners plus the total hash rate of new transactions.

\section{Time between blocks}

The hash function used for the proof-of-work (PoW) is the same as Bitcoin: \emph{SHA-256} applied twice. Thus, most of the math analysis we have done before is just the same.

Let $X$ be the number of trials to solve the PoW and $T$ be the time between blocks. We already know that $X$ follows a geometric distribution with $p = \frac{A}{2^{256}}$, where $A$ is inversely proportional to the difficulty, i.e., the smaller the $A$, the higher the difficulty. We also know that $T$ follows an exponential distribution with $\lambda = \frac{1}{\eta}$, where $\eta$ is the average time between blocks. As proved before, $\eta p H = 1$, thus let's define $w = \log_2(\mathbf{E}(X)) = \log_2(1/p) = \log_2(\eta H) = \log_2(\eta) + \log_2(H)$.

For the blocks, $\eta = 128$, thus, $\mathbf{E}(T) = 128 \text{ seconds}$, and $\mathbf{V}(T) = 16,384$. The symmetrical confidence interval with $\alpha = 10\%$ is $[6.56, 383.45]$, i.e., 90\% of the cases the distance between blocks will be between 6 seconds and just under 7 minutes.

Let $H$ be the hash rate of the miners, then, the weight of the blocks is calculated by

$$w_\text{blocks} = \log_2(128) + \log_2(H) = 7 + \log_2(H)$$

This weight will be updated every 2,016 blocks to take into consideration the change of $H$. First, $H$ will be estimated using the fact that $\mathbf{E}(Y_{2016}) = \frac{2016}{\lambda} = 2016 \eta = \frac{2016}{pH} = \frac{2016 \cdot 2^w}{H}$. Thus, $H = \frac{2016 \cdot 2^w}{\Delta t} \Rightarrow \log_2(H) = w + \log_2(2016) - \log_2(\Delta t)$, where $\Delta t$ is the time between the latest weight update and now. Finally,

$$w_\text{new} = 7 + w_\text{old} + \log_2(2016) - \log_2(\Delta t)$$

Notice that, if the hash rate does not change, then $\Delta t = 128 \cdot 2016$ and $w_\text{new} = w_\text{old}$.

\section{Weight of the transactions}

There is a trade-off which must be considered in the weight of the transactions: the higher the weight, the better to prevent spams, but the worse to microtransactions. So, trying to fulfill both necessities, the weight will be a function of the transaction's size (in bytes) and total amount:

$$w_\text{tx} = \left\lfloor \log_2(\text{size}) + \log_2(\text{amount}) + 0.5 \right\rfloor$$

Although the transaction size may change a bit depending on the implementation, a typical transaction with 2 inputs and 2 outputs would have 188 bytes. So, for instance, transfering 50,000 tokens would require a weight of 23, which means an average of $2^{23}$ trials to solve the PoW.

\section{Issuance rate}

Bitcoin issuance rate started in 50 tokens per block and decreases over time. Every 210,000 blocks---4 years, on average---it halves the number of tokens issued per block. As Bitcoin smallest fraction is $10^{-8}$, after the 33th reduction it will stop issuing new tokens since $2^{33} > 50 \cdot 10^{-8}$. In total, the number of issued tokens will never exceed 21 million. For further information, see \cite{bitcoinsupply}.

Using the same strategy, Hathor's issuance rate starts in 50,000 tokens per block and decreases over time. Different from Bitcoin, Hathor's tokens are always integers and cannot be split. Every 1,000,000 blocks, the number of tokens issued per block is halved. Thus, the supply is limited to 100 billion issued tokens during its whole life. To calculate the supply limit use the following equation:

\begin{align*}
    \sum_{k=0}^{\infty} 1,000,000 \cdot \left\lfloor \frac{50000}{2^k} \right\rfloor \approx
    \sum_{k=0}^{\infty} 1,000,000 \cdot \frac{50000}{2^k} = 100 \text{ billion}
\end{align*}

As the average time between blocks is 128 seconds, it will take around 3 years, 9 months and 20 days between halves.

\section{Transaction fees}

The value of the fee is calculate as the difference between the transaction's outputs and the inputs. For instance, a transaction with inputs summing 10,000 HTR and outputs summing 9,000 HTR are paying 1,000 HTR of fees.

Each transaction may pay a fee to the next block which confirms it. But, even if the fee is zero, the miners are forced to confirm at least two pending transactions (in-progress or unconfirmed), and these pending transactions confirms other transactions which may have no fees. In summary, transactions with no fees cannot be left behind and will always be confirmed by both blocks and other transactions.

One may arguee that it allows the whole network to never pay fees and they are right. In the beginning, miners' incentive is driven by new tokens instead of fees. In the long term, it may be necessary to require a minimum fee to keep the miners working.

\section{Transaction validation}

A transaction will be considered valid when it complies with the following rules: (i) it spends only unspent outputs; (ii) the sum of the inputs is greater than or equal to the sum of the outputs; (iii) the number of inputs is at most 256; (iv) the number of outputs is at most 256; (v) it confirms at least two pending transactions; (vi) it solves the PoW with the correct weight.

The transaction has a time field which is used to inform when the transaction was generated. The time field must be in UTC time and may be within at most 60 minutes from the current time. Otherwise, the transaction will be discarded.

In case of transaction conflict, in which two transactions try to spend the same tokens, the one with higher accumulated weight is chosen and the other is invalidated. Although it is not possible in Iota because of the submarine attack, Hathor does not have the same problem. In Hathor, like in Bitcoin, the submarine attack is only possible if the attacker has a hash rate higher than the whole network, including the miners. In other words, when analysing the double spending attack, Hathor is as safe as Bitcoin.

The digital signature is used to ensure that only the owners may spend their tokens. It will be calculated signing the transaction's input and output only. This allows the transaction to be signed in one device and to be sent to another device that will choose which transaction will be confirmed and will solve the proof-of-work.

Services of solving proof-of-work may also be offered by companies. They give their customers a wallet address and they send the payment inside of the transaction itself. This allows IoT devices to save energy or to delegate the task of solving the PoW to whoever is receiving the tokens.

\section{Orphan blocks}

There is no orphan blocks in Hathor. Unless a block confirms either directly or indirectly an invalid transaction, every block is valid. There is no need to left a block behind since its proof-of-work is also protecting transactions.

\section{Network}

Like in all other cryptocurrencies, nodes will communicate through a peer-to-peer network. They will exchange transactions and blocks, verifying whether they are valid or not, while they will also answer queries.

Thus, if a thin client wants to transfer some tokens, it just connects to the network and queries for the tips. With the response, it solves the proof-of-work and propagates the new transaction. In order to avoid malicious nodes, the thin client may ask to more than one node and randomly pick two transactions.

\chapter{Proposal: Questions to be explored}

@@

In this paper, we will analyze the network scaling and security. How a Hathor network scales, simulating different loads and measuring the bandwidth, computational effort, and storage space necessary to handle all the transactions in time. What is the minimum transaction's aggregated weight which it may be considered unlikely to be reversed?

@@

What is better: solves a PoW with $w$, or solves $n$ PoWs with $w/n$?

%\cite{tangle2016} suggests that constraining transactions' weight in a range would both prevent spam, because it would be necessary a minimum work to propagate a new transaction, and attacks, because an attacker would not be allowed to propagate a transaction with very high weight. We agree with the spam argument, and would like how a minimum weight would affect mobile devices's new transactions. We partially agree with the upper bound, because an attacker would be able to generate many transaction with lower weight. We will analyze if constraining transactions' weight would be effective against nuclear submarine attacks.

%We have another suggestion to prevent nuclear submarine attacks: set a maximum depth for the transactions confirmed by a new transaction. So, new transactions would have to confirming newer transactions instead of old transactions, and a nuclear submarine attack would be controlled because the attacker would be not be able to create a large separate DAG. But the maximum depth rule would possibly also affect transaction created by low (hash)power devices, because it would take a longer time to solve the proof-of-work and, if the confirmations are going fast, the transaction would possibly be invalidated. This raises another important question: what would be an optimal maximum depth allowed?

%If we would like to include fee transactions, how would it be distributed between confirmations? As transactions may have multiple direct confirmations, it is not obvious who would receive the transaction fee. An intuitive suggestion would be to give the fee to the first confirmation with a minimum weight, but it might have some propagation problems, because it takes a while to propagate a transaction in the network and there would be conflict.

%In order to solve the fee distribution problem, we will simulate how the network would behave if we include blocks. These blocks would be like Bitcoin's, with an adjustable proof-of-work according to the network's hashpower. They would receive the fees from all confirmed transactions which had not been confirmed by any block before, and they would be able to generate new coins. These blocks would also help solving other problems.

@@

\chapter{Analysis of Hathor}
